The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-09 paper/ms.tex
sections 3.4 and 3.5 done

Figure \ref{fig:Nscatt2D} supports our hypothesis about
the photo-sphere in the homogeneous distribution. In that case most of
the photons that left with $x\sim 0$ have escaped with less than $10$
scatterings. This explains the origin of a single central
peak. However, for a central distribution the situation is
different. In this case the number of scatterings remains high, in the
order of the optical depth, but the two peaks do get closer to each
other. In this case the physical picture is that each scattering, due
to the bulk velocity of the gas, is inefficient in driving the photon
outside the line center.

@@

Figure \ref{fig:OCspheres} shows the two spherical regions we
define to test for this effect. Each has a radius of $0.5$R and can
have two possible centers positions $C$ along the $\hat{\j}$ direction:
$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
direction, such that the emitting sphere centered on $+C\hat{\j}$ moves
away from the observer and the sphere centered on $+C\hat{\j}$ moves
towards the observer. We consider $C=0.5 R$.

We study first the angular deviations of the outgoing photons with respect
to an isotropic flux. We follow \cite{Zheng2013} to estimate the flux
as a function of the angle $\Theta$ formed by the outgoing photons and
a the observer. This is expressed by

@@

In the off-center emission the variations in the $\mu$ distribution
$\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
 $\Delta \mu \leq 7\%$; $V_{\rm max}=100$\kms, $\Delta \mu\leq 12\%$
and $V_{\rm max}=200$\kms, $\Delta\mu\leq 15\%$ (NOTE: regardless of
$\tau$??). This implies a strong dependence of the observed flux on
the relative position of an observer.  In contrast,the central and
homogeneous source distributions only show a weak anisotropy at the level of
$\Delta\mu\leq 3\%$.

Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer ($\vert \mu \vert > 
0.9$ $\&$ $\vert \mu \vert < 1.0]$).  We do not find any asymmetry in 
the line produced by the off-center emission, The difference
 between the profiles corresponding to the spheres located at $C=-0.5R$ 
 and that ones located at $C=0.5R$ is negligible.  As in the homogeneous / 
central model the line gets broader as the rotational velocity also 
the central part of the line becomes predominant . 
There is also a signature of possible three peaks profiles for  some models ($\tau = 10^6,
V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) which would be studied 
in detail in the Sec.\ref{sec:3p}

\begin{figure}
\includegraphics[scale=0.35]{mu_OC.png} \caption{Flux angular 
  dependency for off-center distribution. Different line widths
  illustrate different rotational velocities.\label{fig:OCflux}} 
\end{figure}

@@

\subsection{Three-Peak Profiles}
\label{sec:3p}
\begin{figure*}
\includegraphics[scale=0.3]{3peaks.png}
\caption{Three-Peak profiles for the off-center positions. 
   \label{fig:3p_profiles}} 
\end{figure*}

As mentioned in Sec\ref{sec:off-center} Off-centered emission shows signs of three peak 
profiles, to analyse this in more detail we use the same method of the spheres
explained in that section. We select spheres at $C=\pm 0.25R, 0.5R, 0.75R$ with a radii of
$0.25R$ for all the models, for those who present signs of three peak profiles such as 
$(V_{max}=50kms^{1} \& \tau_{H}=10^{5}), (V_{max}=100kms^{1} \& \tau_{H}=10^{6}), 
(V_{max}=200kms^{1} \& \tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
with the aim of get a stronger profile.

Fig. \ref{fig:3p_profiles} shows our findings, in order to get such profiles 
a relation between optical depth, rotational velocity and $C$ must be accomplish.
In particular we found that for the outer spheres $C=\pm 0.75$ the three
peak arises for all of our models with $\tau_{\gamma}=10^{6}$ this is due to 
the fact that the wings of the line move away from the central part as $C$ increase. 
Another requirement is that a high optical must be balanced with a high velocity 
in order to make the wings and the central peak similar in 
height.

>>>>

The top right panel of Figure \ref{fig:Nscatt2D} supports our hypothesis about
the photo-sphere in the homogeneous distribution. In that case most of
the photons that left with $x\sim 0$ have escaped with less than $10$
scatterings. This explains the origin of a single central
peak. However, for a central distribution the situation is
different. In this case the number of scatterings remains high, in the
order of the optical depth, but the two peaks do get closer to each
other. In this case the physical picture is that each scattering, due
to the bulk velocity of the gas, is inefficient in driving the photon
outside the line center.

@@

Figure \ref{fig:OCspheres} shows the two spherical regions we
define to test for this effect. Each has a radius of $0.5$R and can
have two possible centers positions $C$ along the $\hat{\j}$ direction:
$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
direction, such that the emitting sphere centered on $+C\hat{\j}$ moves
away from the observer and the sphere centered on $+C\hat{\j}$ moves
towards the observer.

We study first the angular deviations of the outgoing photons with respect
to an isotropic flux. We follow \cite{Zheng2013} to estimate the flux
as a function of the angle $\Theta$ formed by the outgoing photons and
the observer. This is expressed by

@@

\begin{figure}
  \includegraphics[scale=0.35]{muhisto.png}
  \caption{$\mu$ histogram showing the orientation effects for the different
  distributions Central(Points line), Homogeneous(Dashed) and Off-Center(Solid line).  
    \label{fig:muhisto}} 
\end{figure}

The variations in the $\mu$ distribution is shown in Fig.\ref{fig:muhisto},
for the Off-Center model there is a strong dependence of the 
observed flux on the relative position of an observer with $\Delta\mu\leq 25\%$.
In contrast,the central and homogeneous source distributions only show a 
weak anisotropy at the level of $\Delta\mu\leq 3\%$. On the other hand the variations
in $\mu$ does not depend on the rotational velocity while increasing the optical depth $\tau_{H}$
would also increase the variation of $\Delta\mu$ up to a $15\%$.

Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer ($\vert \mu \vert > 
0.9$ $\&$ $\vert \mu \vert < 1.0]$).  We do not find any asymmetry in 
the line produced by the off-center emission, The difference
 between the profiles corresponding to the spheres located at $C=-0.5R$ 
 and that ones located at $C=0.5R$ is negligible.  As in the homogeneous / 
central model the line gets broader as the rotational velocity increase also 
the central part of the line becomes predominant . 
There is also a signature of possible three peaks profiles for some models ($\tau = 10^6,
V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) which would be studied 
in detail in the Sec.\ref{sec:3p}

@@

\subsection{Three-Peak Profiles}
\label{sec:3p}

\begin{figure*}
\includegraphics[scale=0.3]{3peaks.png}
\caption{Three-Peak profiles for the off-center positions. 
   \label{fig:3p_profiles}} 
\end{figure*}

As mentioned in Sec\ref{sec:off-center} Off-centered emission shows signs of three peak 
profiles, to analyse this in more detail we use the same method of the spheres
explained in that section. We select spheres at $C=(\pm 0.25R, \pm0.5R, \pm0.75R)$ with a radii of
$0.25R$ for all the models, for those who present signs of three peak profiles such as 
$(V_{max}=50kms^{1}$ \& $\tau_{H}=10^{5}), (V_{max}=100kms^{1}$ \& $\tau_{H}=10^{6}), 
(V_{max}=200kms^{1}$ \& $\tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
with the aim of get a stronger profile.

Fig. \ref{fig:3p_profiles} shows our findings, in order to get such profiles 
a relation between optical depth, rotational velocity and $C$ must be accomplish.
In particular we found that for the outer spheres $C=\pm 0.75$ the three
peak arises for all of our models with $\tau_{\gamma}=10^{6}$ this is due to 
the fact that the wings of the line move away from the central part as $C$ increase. 
Another requirement is that a high optical depth must be balanced with a high velocity 
in order to make the wings and the central peak similar in 
height.
